Motion planning for assessing accessibility of protein tunnels

### 2017-09-10 paper.tex
final image

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{fig/dcp-image1Label}\\
\includegraphics[width=0.2\textwidth]{fig/colormap}
\caption{\label{fig::dcp}
Visualization of trajectories for the ligand DCP   in the two examined tunnels.  
    The color of the trajectories corresponds to the scale, that was needed to pass the given part of the tunnel.
    For the purpose of this image, also scales $\smin=0.3$ and $\smin=0.4$ where tested.
}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{fig/dcp-image1Label}\\
\includegraphics[width=0.2\textwidth]{fig/colormap}
\caption{\label{fig::dcp}
Visualization of trajectories for the ligand DCP   in the two examined tunnels.  
The color of the trajectories corresponds to the scale, that was needed to pass the given part of the tunnel.
The ligand can enter the first tunnel with a high scale (almost 1=100~\%) (A), but then it has to scale-down (to $\sim75$~\%) to pass the
next part of the tunnel (B). After this narrow passage, the tunnel is larger and the ligand can traverse to the narrow passage with
scale $>75$~\% (C).
The second tunnel can also be entered with the high scale (green), but then the narrow part is traversable only with a low scale ($\sim50$~\%) (D). 
For the purpose of the visualization, even more scale-down to 0.3=30~\% was allowed (E) to see how the ligand pass the tunnel.
However, the ligand can reach the active site only with very low scale ($\sim0.4=40$~\%) using the second tunnel.
}
\end{figure}
